Data preparation

### 2024-03-19 procesamiento/02-prod_prep-macro.Rmd
ajustes welfare state variables

@@

```{r merge}
macro_data <- 
  left_join(wiid_2017,solt_2017) %>%
  left_join(pen_2017) %>% 
  left_join(otero) %>%
  left_join(ocde) %>% 
  left_join(wid_df1)

>>>>

**ILO Data**

```{r}
ilo_data <- read.csv(file = here::here("input/data/original/ILO-data/WEOApr2022all.csv"))
frq(ilo_data$Subject.Descriptor)

ilo_data_1 <- ilo_data %>% filter(Subject.Descriptor %in% c("General government total expenditure","General government revenue"), Units == "Percent of GDP")
ilo_data_1$ccode <- countrycode::countrycode(sourcevar = ilo_data_1$ISO,origin = "iso3c",destination = "iso3n") 
ilo_data_1<- ilo_data_1 %>% filter(ccode %in% countries$ccode)
ilo_data_1 <- ilo_data_1 %>% select(ccode,WEO.Country.Code:Country.Series.specific.Notes,X2010:X2020)
names(ilo_data_1) <- tolower(names(ilo_data_1))
names(ilo_data_1) <- str_replace_all(string = names(ilo_data_1),pattern = "x",replacement = "Y_")

ilo_tax <- ilo_data_1 %>% filter(weo.subject.code=="GGR_NGDP") 
ilo_spe <- ilo_data_1 %>% filter(weo.subject.code=="GGX_NGDP") 
# Example wide format data

# Convert from wide to long format
long_ilo_tax <- ilo_tax %>%
  select(ccode,Y_2010:Y_2016) %>% 
  pivot_longer(cols = starts_with("Y_"),
               names_to = "year",
               names_prefix = "Y_",
               values_to = "ilo_taxrev")
# long_ilo_tax$country <- countrycode::countrycode(sourcevar = long_ilo_tax$ccode,origin = "iso3n",destination = "iso3c")

long_ilo_spe <- ilo_spe %>%
  select(ccode,Y_2010:Y_2016) %>% 
  pivot_longer(cols = starts_with("Y_"),
               names_to = "year",
               names_prefix = "Y_",
               values_to = "ilo_govspe")

ilo_df <- left_join(long_ilo_tax,long_ilo_spe) %>% filter(year==2016)

# long_ilo_spe$country <- countrycode::countrycode(sourcevar = long_ilo_spe$ccode,origin = "iso3n",destination = "iso3c")

# Plot points connected by a line representing time
# ggplot(long_ilo_spe, aes(x = factor(year), y = govspe, group = factor(country), color = factor(country))) +
#   geom_line() +
#   geom_point(size = 3) +
#   labs(title = "Points Connected by a Line Representing Time", x = "Year", y = "Value") +
#   # scale_x_discrete(labels = c("2016", "2017", "2018")) +
#   theme_minimal()
# 
# 
# # Plot points connected by a line representing time
# ggplot(long_ilo_tax, aes(x = factor(year), y = taxrev, group = factor(country), color = factor(country))) +
#   geom_line() +
#   geom_point(size = 3) +
#   labs(title = "Points Connected by a Line Representing Time", x = "Year", y = "Value") +
#   # scale_x_discrete(labels = c("2016", "2017", "2018")) +
#   theme_minimal()

```

@@

```{r merge}
macro_data <- 
  left_join(wiid_2017,solt_2017) %>%
  left_join(pen_2017) %>% 
  left_join(otero) %>%
  left_join(ocde) %>% 
  left_join(wid_df1) %>% 
  left_join(ilo_df)
